Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-23 CONCUR2018/paper.tex
Minor fixes

In order to show the improvements due to our optimization-enhanced
CEGIS, we compared our approach against the CEGIS approach with
abstraction refinement described
in~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  We note that,
while~\cite{DBLP:conf/cav/AbateBCCDKKP17} presents two approaches, one
of them (referred to as the naive approach
in~\cite{DBLP:conf/cav/AbateBCCDKKP17}) cannot handle the continuous
time case and thus we can only compare against the abstraction-based
one (referred to as CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17} in Table~\ref{tab:cegis_results}).  %% Furthermore, since it is in general slower than the abstraction
%% refinement version, the latter is a more representative benchmark).
For the majority of our benchmarks, we observe that our approach is
significantly faster than CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  %% We
%% further note that the number of times CEGIS times out is much larger
%% than CEGIS-OR which results in more found solutions.

>>>>

In order to show the improvements due to our optimization-enhanced
CEGIS, we compared our approach against the CEGIS approach with
abstraction refinement described
in~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  We note that,
while~\cite{DBLP:conf/cav/AbateBCCDKKP17} presents two approaches, one
of them (referred to as the naive approach
in~\cite{DBLP:conf/cav/AbateBCCDKKP17}) cannot handle the continuous
time case and thus we can only compare against the faster, abstraction-based
one (referred to as CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17} in Table~\ref{tab:cegis_results}).  %% Furthermore, since it is in general slower than the abstraction
%% refinement version, the latter is a more representative benchmark).
For the majority of our benchmarks, we observe that our approach is
significantly faster than CEGIS~\cite{DBLP:conf/cav/AbateBCCDKKP17}.  %% We
%% further note that the number of times CEGIS times out is much larger
%% than CEGIS-OR which results in more found solutions.
